Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-04 mu/article/article.tex
Reorganization of sections.

\subsection{Pure spin-current} % (fold)
\label{sec:theory-pure_spin_current}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin spin Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Fixing spin} % (fold)
\label{sec:res-fixspin}

@@

% %% Description of ALT layer |V^{yz}|
% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
% %%         alt-plots/alt-vab-layers.gp
\begin{figure}[tb]
    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
     \emph{alt} structure.}
    \label{fig:alt-vyz-lay}
From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
the \emph{alt} structure the most intense component of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.2\,Km/s for an
energy incident beam of 0.72\,eV. This component and the corresponding layer by
layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
in the same direction resulting in a total response
$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
0.912\,eV.
    \subfigure[\ \label{fig:up-vyz-lay-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}
    \subfigure[\ \label{fig:up-vyz-lay-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
     \emph{up} structure.}
    \label{fig:up-vyz-lay}
% %% Description of ALT layer |V^{yz}|
% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
% %%         alt-plots/alt-vab-layers.gp
From the bottom frames of Figs. \ref{fig:up-vab-comp-rtp-1} and 
\ref{fig:up-vab-comp-rtp-2} we can see that for the \emph{up} structure again
the most intense component of $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$ corresponds to $\mathcal{V}^{\mathrm{yz}}$ which
has a value of 87.2\,Km/s for an energy incident beam of 0.088\,eV and
-29.7\,Km/s for an energy incident beam of 1.972\,eV. This component and the
corresponding layer by layer contribution is depicted in Fig. 
\ref{fig:up-vyz-lay}s.
From this figure we have that for the energy range from 0\,eV to 0.2\,eV the
response comes from the second layer composed by carbon atoms presented in Tab.
\ref{tab:up-unitcell} and denoted by the number 2 in Fig. \ref{fig:up-struc}. In
the other hand, the response for the energy range from 1.8\,eV to 2.1\,eV almost
all the response comes from the carbon atoms having a leaser contribution from
the hydrogen layer.

>>>>

\subsection{Pure spin velocity} % (fold)
\label{sec:theory-pure_spin_current}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: mu & V^{ab} comparison %%%%%%%%%%%%%%%%%%%%%%%

\subsection{Spin velocity} % (fold)
\label{sec:res-pure_spin_current_and_spin_velocity}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{plots/vab-str-comp}
    \caption{Comparison of most intense responses for
    $\mathcal{V}^{\mathrm{ab}}$ for \emph{alt}, \emph{up}, CdSe, and GaAs structures}
    \label{fig:vab-str-comp}
\end{figure}

In figure \ref{fig:vab-str-comp}

% section res-pure_spin_current_and_spin_velocity (end)

@@

\subsection{Fixing spin} % (fold)
\label{sec:res-fixspin}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% Res: Layer-by-layer  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Layer-by-layer analysis} % (fold)
\label{sec:res-layer_by_layer_analysis}

% %%%%%%%%%%%%%%%%
% %% Description of Up layer |V^{yz}|
% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_12802_1_40-spin_scissor_0_Nc_18_ang_40
% %%         calv.sm_0.03_yz_12802_2_40-spin_scissor_0_Nc_18_ang_40
% %%         up-plots/up-vab-layers.gp
% %%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ \label{fig:up-vyz-lay-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-1}}
    \\
    \subfigure[\ \label{fig:up-vyz-lay-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyz-layers-2}}
    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
     \emph{up} structure.}
    \label{fig:up-vyz-lay}
\end{figure}

From the bottom frames of Figs. \ref{fig:up-vab-comp-rtp-1} and 
% 
\ref{fig:up-vab-comp-rtp-2} we can see that for the \emph{up} structure again
the most intense component of $|\mathcal{V}^{\mathrm{x}}|$ and
$|\mathcal{V}^{\mathrm{y}}|$ corresponds to $\mathcal{V}^{\mathrm{yz}}$ which
has a value of 87.2\,Km/s for an energy incident beam of 0.088\,eV and
-29.7\,Km/s for an energy incident beam of 1.972\,eV. This component and the
corresponding layer by layer contribution is depicted in Fig. 
\ref{fig:up-vyz-lay}s.
% 
From this figure we have that for the energy range from 0\,eV to 0.2\,eV the
response comes from the second layer composed by carbon atoms presented in Tab.
\ref{tab:up-unitcell} and denoted by the number 2 in Fig. \ref{fig:up-struc}. In
the other hand, the response for the energy range from 1.8\,eV to 2.1\,eV almost
all the response comes from the carbon atoms having a leaser contribution from
the hydrogen layer.
% %%%%%%%%%%%%%%%%
% %% Description of ALT layer |V^{yz}|
% %% files:  v.sm_0.03_yz_14452_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_1_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_2_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_3_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_4_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_5_65-spin_scissor_0_Nc_32_ang_145
% %%         calv.sm_0.03_yz_14452_6_65-spin_scissor_0_Nc_32_ang_145
% %%         alt-plots/alt-vab-layers.gp
% %%%%%%%%%%%%%%%%
From the bottom frames of Fig. \ref{fig:alt-vab-comp-rtp} we can see that for
the \emph{alt} structure the most intense component of
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ corresponds to
$\mathcal{V}^{\mathrm{yz}}$ which has a value of -40.2\,Km/s for an
energy incident beam of 0.72\,eV. This component and the corresponding layer by
layer contribution is depicted in Fig. \ref{fig:alt-vyz-lay}. From this figure
we have that for the energy range from 0.70\,eV to 0.74\,eV the fifth and sixth
layers corresponding to the bottom carbon and hydrogen numbered with 5 and 6 in
Fig. \ref{fig:alt-struc} have contributions in opposite direction than the other
4 layers resulting in a total response $\mathcal{V}^{\mathrm{yz}}= -40.2$\,Km/s
for an incoming beam energy of 0.72\,eV. In the other hand, for the energy range
from 0.88\,eV to 0.95\,eV the response for the all six layers the responses are
in the same direction resulting in a total response
$\mathcal{V}^{\mathrm{yz}}=-32.89$\,Km/s for an incoming beam with energy of
0.912\,eV.
\begin{figure}[b]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vyz-layers}
    \caption{Layer-by-layer contribution of $\mathcal{V}^{\mathrm{yz}}$ for the
     \emph{alt} structure.}
    \label{fig:alt-vyz-lay}
\end{figure}

% section res-layer_by_layer_analysis (end)
